# Topic 4 Exercises: Classification

4.7.1
If we declare the logistic function to be P(x) then by the calculating the odds, we can find the logit function is P(x)/(1-P(x))... after cancellation, we can see that the e^(B0+B1x) = (e^B0+B1x)/(1+e^B0+B1x)

4.7.8
If K=1 in the KNN regression, then the training error is 0%. That means that the test error is 36%, since the test error is significantly higher in the KNN, it is better to use the logisitic function. 

4.7.9
P(x)/1-P(x) <- P(x)/1+P(x)
```{r}
0.37/(1+0.37)
0.16/(1-0.16)
```

4.7.11
```{r}
library(ISLR)
attach(Auto)
mpg01 <- rep(0,length(mpg))
mpg01[mpg > median(mpg)] <- 1
Auto <- data.frame(Auto, mpg01)
```

```{r}
#b

boxplot(cylinders ~ mpg01, data = Auto, main = "Cylinders vs mpg01")
boxplot(displacement ~ mpg01, data = Auto, main = "Displacement vs mpg01")

boxplot(weight ~ mpg01, data = Auto, main = "Weight vs mpg01")
boxplot(acceleration ~ mpg01, data = Auto, main = "Acceleration vs mpg01")
boxplot(year ~ mpg01, data = Auto, main = "Year vs mpg01")

```
It looks like displacement and Weight are both good predictors of mpg01.

c. 
```{r}
train <- (year %% 2 == 0)
training <- Auto[train, ]
testing <- Auto[!train, ]
mpg01.test <- mpg01[!train]
#d
#fit.lda <- lda(mpg01 ~ cylinders + weight + displacement + horsepower, data = Auto, subset = train)
#fit.lda
#ldap <- predict(fit.lda, data = testing)
#mean(ldap$class != mpg01.test)

```
There is a testing error of 39.4%

e.
```{r}
#fit.qda <- qda(mpg01 ~ cylinders + weight + displacement + horsepower, data = Auto, subset = train)
#fit.qda
#pred.qda <- predict(fit.qda, testing)
#table(pred.qda$class, mpg01.test)
#mean(pred.qda$class != mpg01.test)
```
Code was not working for qda.

f. 
```{r}
fit.glm <- glm(mpg01 ~ cylinders + weight + displacement + horsepower, data = Auto, family = binomial, subset = train)
#summary(fit.glm)
probs <- predict(fit.glm, type = "response")
pred.glm <- rep(0, length(probs))
pred.glm[probs > 0.5] <- 1
#table(pred.glm, mpg01.test)
mean(pred.glm != mpg01.test)
```
The error for testing was 46.6%
g.
```{r}
train.X <- cbind(cylinders, weight, displacement, horsepower)[train, ]
test.X <- cbind(cylinders, weight, displacement, horsepower)[!train, ]
train.mpg01 <- mpg01[train]
set.seed(1)
#pred.knn <- knn(train.X, test.X, train.mpg01, k = 1)
#table(pred.knn, mpg01.test)
#mean(pred.knn != mpg01.test)
#pred.knn <- knn(train.X, test.X, train.mpg01, k = 10)
#table(pred.knn, mpg01.test)
#mean(pred.knn != mpg01.test)
#pred.knn <- knn(train.X, test.X, train.mpg01, k = 100)
#table(pred.knn, mpg01.test)
#mean(pred.knn != mpg01.test)
```
KNN function was not debugging. 

4.7.13
```{r}
library(MASS)
attach(Boston)

crim01 <- rep(0, length(crim))
crim01[crim > median(crim)] <- 1
Boston <- data.frame(Boston, crim01)

train <- 1:(length(crim) / 2)
test <- (length(crim) / 2 + 1):length(crim)
Boston.train <- Boston[train, ]
Boston.test <- Boston[test, ]
crim01.test <- crim01[test]

fit.glm <- glm(crim01 ~ . - crim01 - crim, data = Boston, family = binomial, subset = train)
probs <- predict(fit.glm, Boston.test, type = "response")
pred.glm <- rep(0, length(probs))
pred.glm[probs > 0.5] <- 1
table(pred.glm, crim01.test)
mean(pred.glm != crim01.test)
```
Error term seems to be 0
```{r}
fit.glm <- glm(crim01 ~ . - crim01 - crim - chas - nox, data = Boston, family = binomial, subset = train)
probs <- predict(fit.glm, Boston.test, type = "response")
pred.glm <- rep(0, length(probs))
pred.glm[probs > 0.5] <- 1
table(pred.glm, crim01.test)
mean(pred.glm != crim01.test)
```
```{r}
#fit.lda <- lda(crim01 ~ . - crim01 - crim, data = Boston, subset = train)
#pred.lda <- predict(fit.lda, Boston.test)
#table(pred.lda$class, crim01.test)
#mean(pred.lda$class != crim01.test)
```

```{r}
#train.X <- cbind(zn, indus, chas, nox, rm, age, dis, rad, tax, ptratio, black, lstat, medv)[train, ]
#test.X <- cbind(zn, indus, chas, nox, rm, age, dis, rad, tax, ptratio, black, lstat, medv)[test, ]
#train.crim01 <- crim01[train]
#set.seed(1)
#pred.knn <- knn(train.X, test.X, train.crim01, k = 1)
#table(pred.knn, crim01.test)
#mean(pred.knn != crim01.test)
```
```{r}
#pred.knn <- knn(train.X, test.X, train.crim01, k = 10)
#table(pred.knn, crim01.test)
#mean(pred.knn != crim01.test)
```
```{r}
#pred.knn <- knn(train.X, test.X, train.crim01, k = 100)
#table(pred.knn, crim01.test)
#mean(pred.knn != crim01.test)
```

